\huge Tor's Usability for Censorship Circumvention

### 2016-04-18 pets2017-paper/pets2017-paper.tex
discussion section and other tweaks.

\subsection{Methodology} 
This section shows the details of our quantitative user study, such as the censorship environments we placed our users in, how we recruited our 124 participants, and the procedure for the experiment.

@@

\subsection{Results} 
Out of our 124 participants,  we have 116 valid data points. {\color {red} TODO} participants downloaded their own version of Tor, and {\color {red} TODO} participants did not sign the consent form. We have 58 valid participants who tested the new interface, and 58 who tested the old interface. 38 participants were in E1, 38 participants were in E2, and 40 participants were in E3. Table~\ref{table:participant-summary} summarizes participants' success based on their interface version and environment combination.

Talk about why we chose to assign the max time of 40 minutes to did not finish. 
The impact of the version on time to completion is (significant,not significant). 
The impact of the environment on time to completion is (significant,not significant).
Figure~\ref{fig:time_to_success_clamped}

%stats
impact of version on success: not significant (W = 5.5, p-value = 0.8248)
impact of version on time to success: not significant (W = 1399, p-value = 0.1175)

impact of env on success: not significant (Kruskal-Wallis chi-squared = 4.7059, df = 2, p-value = 0.09509)
impact of env on time to success : significant ( Kruskal-Wallis chi-squared = 80.926, df = 2, p-value < 2.2e-16)

@@

@@

@@

\section{Discussion}

@@

Talk about the notion of ``active time,'' which is just time not spent on the progress screen. 
The impact of the version on active time is significant (W = 997, p-value = 0.0001571)
The impact of the environment on active time is significant (Kruskal-Wallis chi-squared = 51.978, df = 2, p-value = 5.166e-12)

@@

% impacts of making the proxy page ``automated'' 
New people still spent time configuring their proxy!

% impacts of making bridge page collapsed 
This is unclear.

% impacts of giving people advice on which transport to choose.
10 people in the new interface chose meek as their second bridge (10/15, 66\%). 
5 people in the old interface chose meek as their second bridge (5/13, 38\%).

% impacts of adding in a summary page 
adding in a summary screen causes people to think about their configuration.
summary to bridge settings: 13 \% (15/119)
summary to progress: 86 \% (102/119)
summary to summary: 1 \% (2/119)

%FAILURES
Elaborate on why people failed:  
\begin{enumerate}
\item only tried connecting directly (8/23)
\item didn't know what to do after connecting directly and default bridge (6/23)
\item Thought that they needed a proxy (6/23)
\item used the bridges auto-responder incorrectly (3/23)
\end{enumerate}

These non-conservative changes may be helpful for a user, and would benefit from future research: \\

\begin{description}
\item {\bfseries Tell people what to do.} Since a majority of the users will succeed if they click connect on the first screen, replacing the information about choices with explicit instructions to connect can lessen their cognitive load during the configuration process. 
\item{\bfseries Hide infrequently used options.} Hide the proxy screen and do not the option to configure a proxy unless it has been detected as necessary.
\item{\bfseries Tailor for at-risk users.} Currently, the interface is for the average user. We guide at-risk users to the correct configuration, but suggesting that they try the default first. However, this isn't ideal. 
\end{description}

Mention of people downloading their own Tor.

@@

\begin{description}
\item{\bfseries Automate the configuration.} This sounds like a radical idea, but this wouldn't harm users today. Additionally, our study finds that most users would leak that they are using Tor when trying to circumvent an advanced censor. 
\item {\bfseries Automate after failure.} After an unsuccessful connection attempt, the user has already indicated that they are connecting to Tor on the network. Assuming that the significant difference is between being logged trying to connect to Tor or not at all, we can automate the entire configuration process thereafter without increasing risk. This may save our users a lot of headache. 
\item{\bfseries Ask about the risk.} Ask the users if they would be at risk if the process was automated, and automate the configuration process for all who are not at risk. The ones at risk will configure manually. The complication with this approach is that users may not be qualified to answer this question or may not trust Tor to answer honestly. 
\item{\bfseries Ask if users if they know what to do.} We ask users if they know how to configure a bridge and proxy, and automate the configuration process if they do not. However, there are ethical implications of making mistakes on behalf of the users if there is risk involved. 
\end{description}

@@

{\bfseries Cause 1}: only tried connecting directly (8/23): 
\begin{itemize}
\item E2-NEW-X21-20160323-133257 
\item E2-OLD-X04-20160330-181928
\item E2-OLD-X10-20160331-153028
\item E3-NEW-X05-20160324-132535
\item E3-NEW-X17-20160323-133002
\item E3-OLD-X06-20160328-132053
\item E3-OLD-X06-20160330-161525 
\item E3-OLD-X12-20160330-182011
\end{itemize}

{\bfseries Cause 2}: didn't know what to do after connecting directly and default bridge (6/23): 
\begin{itemize}
\item E3-NEW-X11-20160330-161511
\item E3-NEW-X11-20160331-174655
\item E3-NEW-X23-20160323-133346
\item E3-OLD-X06-20160331-174650
\item E3-OLD-X12-20160331-153055
\item E3-OLD-X30-20160328-134412
\end{itemize}

{\bfseries Cause 3}: Thought that they needed a proxy (6/23): 
\begin{itemize}
\item E2-OLD-X10-20160328-132828
\item E3-NEW-X18-20160330-170145
\item E3-NEW-X17-20160328-160037
\item E3-OLD-X06-20160325-175101
\item E3-OLD-X06-20160330-181926
\item E3-OLD-X24-20160328-155926
\end{itemize}

{\bfseries Cause 4}: used the bridges autoresponder incorrectly (3/23): 
\begin{itemize}
\item E3-NEW-X23-20160328-155924 (Figure \ref{autoresponder1})
\item E3-OLD-X12-20160325-140813 (Figure \ref{autoresponder2})
\item E3-OLD-X24-20160328-133857 (Figure \ref{autoresponder3})
\end{itemize}

>>>>

\subsection{Methodology} 
This section details of our quantitative user study, such as the censorship environments we placed our users in, how we recruited our 124 participants, and the procedure for the experiment.

@@

\subsection{Results} 
Out of our 124 recruited participants, 116 provided valid data. We have 58 participants who tested the new interface, and 58 who tested the old interface. 38 participants were in E1, 38 participants were in E2, and 40 participants were in E3. Since our experiment ended after 40 minutes, we chose to assign the max time of 40 minutes to participants who did not succeed. Table~\ref{table:participant-summary} summarizes the rate of success and time to success for our participants' based on their interface version and environment combination.

\subsubsection{Rate of Success} 
Distribution of success times. Figure~\ref{fig:time_to_success_clamped}

%stats
impact of version on success: not significant (W = 5.5, p-value = 0.8248)
impact of env on success: not significant (Kruskal-Wallis chi-squared = 4.7059, df = 2, p-value = 0.09509)

@@

\subsubsection{Time to Success}

impact of version on time to success: not significant (W = 1399, p-value = 0.1175)
impact of env on time to success : significant ( Kruskal-Wallis chi-squared = 80.926, df = 2, p-value < 2.2e-16)

@@

\subsubsection{Additional Information}

@@

@@

Talk about the notion of ``active time,'' which is just time not spent on the progress screen.

@@

% statistical tests
The impact of the version on active time is significant (W = 997, p-value = 0.0001571)
The impact of the environment on active time is significant (Kruskal-Wallis chi-squared = 51.978, df = 2, p-value = 5.166e-12)

\subsection{Discussion} 
This section talks about general trends in user behavior, common failure cases, and our recommendations for 
improving the Tor configuration interface.

\subsubsection{Observations}
These are general observations made from our data set of participants, which may have biases.\\

\begin{description}
%connect vs configure
\item {\bfseries Users try the easy path first.}
81\% (94 of 116) of first attempts were to connect directly, 86\% (50 of 116) from the new interface and 76\% (44 of 116) from the old interface.

% impacts of making the proxy page ``automated'' 
\item {\bfseries Users wasted time configuring proxies.} Overall, 57\% of participants' active time was spent configuring proxies. Participants with the new interface spent 31\% of their active time configuring proxies and participants in the old interface spent 63\%.

% impacts of giving people advice on which transport to choose.
\item {\bfseries Certain transports were chosen with high probability.}
Of those who tried an obfs3 bridge and failed, 
66\% (10 of 15) participants with the new interface and 38\% (5 of 13) participants with the old interface chose meek as their second bridge. Flashproxy was also a popular choice. Many bridges were never chosen.

%error messages
\item {\bfseries There were (almost) no error messages.} Many waited for minutes at the progress screen, but never saw an error message. Only one participant ever saw an error message. We are unable to state the efficacy of our attempts to make error messages more understandable and instructive for lack of data.

% progress bar
\item {\bfseries Users with the new interface waited longer.}
Participants with the new interface the new interface spent more time waiting in the progress bar, proportionally and absolutely. 
\end{description}

It is unclear why users with the new interface chose to configure proxies after explicitly being told that they do not need one, if they chose meek bridges based on our advice, and why they chose to wait longer at the progress screen.

\subsubsection{Reasons for Failure} 
Failure is common. 64\% (74 of 116) of first attempts to connect failed and 79\% (376 of 462) of total attempts to connect failed. Although most participants eventually succeeded, 20\% (23 of 116) failed entirely. Reasons for failure were determined by a combination of log processing (i.e. how much time was spent on a particular screen) and video observation (i.e. observing what they searched for online while they were stuck). \\

\begin{description}
\item {\bfseries Only connected directly. (8/23)} These participants tried a direct connection. When that failed, they tried the same configuration, over and over, without trying other configurations, no matter how many times they failed. It was common to restart the interface, check Internet settings, and wait between subsequent attempts. 
\item {\bfseries Didn't know what to do next. (6/23)} After a failed direct connection and a failed default obfs3 bridge connection, these participants did not know what to do next. They often tried those configurations again or gave up. 
\item {\bfseries Thought that they needed a proxy (6/23)} After a couple failed attempts, these participants assumed that they needed a proxy. They spent the time trying to configure a proxy, usually without trying other bridges. 
\item {\bfseries Used the bridges auto-responder incorrectly (3/23)} Three participants in our heavy censorship environment figured that the recommended bridge and most hard-coded bridges were not working and found the auto-responder through the help button. However, they all failed to get a response. For details, see Appendix~\ref{failed-participants}.
\end{description}

Some participants chose to download their own version of Tor. We discarded these participants' data and do not count this behavior as a failures or success. While some downloaded their own version without trying the provided one on their desktop, others did so after feeling frustrated with the provided version. For unfortunate details of where participants downloaded tor when torproject.org was blocked, see Appendix~\ref{tor-downloads}.

\subsubsection{Recommendations}
Based on our observations of general behavioral trends and common failure cases, we make the following recommendations to increase success rate and decrease overall time spent in the interface: \\

\begin{description}
\item {\bfseries Automate configuration after failure.} After one unsuccessful attempt, the user has already indicated to their censor that they are connecting to Tor. Automating the configuration process thereafter will have no increase in risk, bu can help a majority of users. 64\% of participants who failed their first attempt. Users in more difficult censorship environments are more likely to benefit from this, as 5\% of participants in the mild censorship environment , 84\% participants in intermediate censorship environment, and 100\% of participants in the heavy censorship environment failed the first time.
\item{\bfseries Hide infrequently used options.} Informing users that they did not need a proxy was not enough to deter users from spending time on configuring a proxy. Only a small fraction of the Internet population requires a proxy to connect to the Internet. Hiding the proxy screen by default and only showing it after it has been detected as necessary can focus user efforts on configuring bridges.
\item {\bfseries Be explicit about recommendations.} Being explicit about the order in which a user should choose bridges will result in higher rates of success and lessen cognitive load on the user. Most participants followed recommendations about which bridge to choose, and many did not know what to do after the recommended bridge failed. 
\item{\bfseries Set a timeout.} Informing users that they have failed earlier will decrease the overall time to success, create an opportunity to give suggestions, and reduce user frustration. 
\item{\bfseries Have a user-tolerant auto-responder.} Having the auto-responder default respond with bridges or catching common errors (such as typing ``get bridges'' in the subject line) can help those who need custom bridges. 
\end{description}

We believe that these changes have can greatly help future users connect to the Tor network.

@@

\begin{description}
\item{\bfseries Automate the configuration.} This sounds like a radical idea, but this wouldn't harm users today. Additionally, our study finds that most users would leak that they are using Tor when trying to circumvent an advanced censor. 
\item{\bfseries Ask about the risk.} Ask the users if they would be at risk if the process was automated, and automate the configuration process for all who are not at risk. The ones at risk will configure manually. The complication with this approach is that users may not be qualified to answer this question or may not trust Tor to answer honestly. 
\item{\bfseries Ask if users if they know what to do.} We ask users if they know how to configure a bridge and proxy, and automate the configuration process if they do not. However, there are ethical implications of making mistakes on behalf of the users if there is risk involved. 
\end{description}

@@

Only connected directly (8/23): 
\begin{itemize}
\item E2-NEW-X21-20160323-133257 
\item E2-OLD-X04-20160330-181928
\item E2-OLD-X10-20160331-153028
\item E3-NEW-X05-20160324-132535
\item E3-NEW-X17-20160323-133002
\item E3-OLD-X06-20160328-132053
\item E3-OLD-X06-20160330-161525 
\item E3-OLD-X12-20160330-182011
\end{itemize}

Didn't know what to do next (6/23): 
\begin{itemize}
\item E3-NEW-X11-20160330-161511
\item E3-NEW-X11-20160331-174655
\item E3-NEW-X23-20160323-133346
\item E3-OLD-X06-20160331-174650
\item E3-OLD-X12-20160331-153055
\item E3-OLD-X30-20160328-134412
\end{itemize}

Thought that they needed a proxy (6/23): 
\begin{itemize}
\item E2-OLD-X10-20160328-132828
\item E3-NEW-X18-20160330-170145
\item E3-NEW-X17-20160328-160037
\item E3-OLD-X06-20160325-175101
\item E3-OLD-X06-20160330-181926
\item E3-OLD-X24-20160328-155926
\end{itemize}

Used the bridges auto-responder incorrectly (3/23): 
\begin{itemize}
\item E3-NEW-X23-20160328-155924 (Figure \ref{autoresponder1})
\item E3-OLD-X12-20160325-140813 (Figure \ref{autoresponder2})
\item E3-OLD-X24-20160328-133857 (Figure \ref{autoresponder3})
\end{itemize}
